Teaching a Class to Grade Itself using Game Theory

### 2013-09-26 Primes Write up.tex
Final Changes

\documentclass[12pt, Arial]{article}
\title{Teaching a Class to Grade Itself using Game Theory}
\author{}%Nick Kaashoek and William Wu
\date{}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage[section]{placeins}
\usepackage{enumitem}
\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses) and their importance to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}. However, the main importance of MOOCs come from their scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are simply unable to grade hundreds of thousands of submissions. Currently, two types of solutions are used to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers (i.e. multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}. Even though automated grading for written essays is an active area of research with much recent progress, the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}. On the other hand, peer grading can grade any type of question, a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}. These limitations render the students unable to effectively evaluate the mastery of the course material.

@@

The difficulty of the problem lies in finding an incentive to encourage students to spend time grading the assignments of others. Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example. However, this choice may not return a useful result because a clever student will just take the points and assign a generic grade. The professor cannot tell the difference between an accurately assigned hundred and randomly awarded 100. The next step would be to implement simple checking. For example, have each paper be graded by two students who both receive bonus points if their grades match. This case may work if the students are isolated, but the professor still cannot tell the difference between a randomly or sincerely awarded grade. This way, their papers will match those of other clever students, giving them points without grading. These examples show that properly incentivizing graders can be a difficult task. The main purpose of this work is to devise mechanisms which avoid these problems, allowing for work to be distributed efficiently.

@@

We start with a simple model and set of assumptions and gradually build upon this set to achieve an increasingly-realistic model. After every change in assumptions, we create a new mechanism that works effectively and efficiently. By the end of our research, we have contributed a highly realistic and detailed model that other game theorists can build off of to form their own solutions, as well as a set of realistic mechanisms that could be implemented in practice.
\section{Materials and Methods}
\subsection{Scenario}
In order to find a solution to the professor's problem, we consider the case of a single assignment. To apply our solution to an entire class, simply apply it to each assignment separately. In a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are the input for a function. Each of these papers, $i$ has an objective score $o_i,~where~ 0\leq o_i \leq 100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way, with the grades given out being the functions output. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, we use a set process every time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, we create this set of assumptions:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students want good grades
	\item Doing work makes students unhappy
	\item Students want to be happy
	\item Students only care about their final happiness
	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
To re-express the above in mathematical terms:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
	\item Students can grade others' work accurately (i.e., they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
	\item Students want to maximize their final happiness, expressed as $H(g)-W$
	\item Students care only about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e., if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
	\item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It does not depend on the score of others
\end{enumerate}

@@

\subsection{Objective}
The goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment they are given to grade. Without this property, a system becomes unpredictable. In other words, no student can deviate from the desired behavior to improve his or her happiness. In math terms, if by acting honestly student $i$ grades $w_i$ papers and gets a grade of $g_i$ there should not be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.

\subsection{Benchmark}
%Efficiency objective%
A benchmark that will allow different mechanisms to be compared is vital to the iterative process of mechanism development. Mechanisms should be compared in terms of the relative happiness of people --- which can be expressed as a function of work done --- as well as the accuracy of the grades produced. Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desirable outcome. In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case. This benchmarking function is known as the \emph{Objective function}, which we use in our research.

@@

In our case, we use the \emph{maximum} deviation and the \emph{maximum} work done. The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is as follows. Consider the following two cases for the maximum deviation of the grade assigned by the mechanism to the hypothetical professor-given grade. Note that the grade the student receives at the end is not necessarily that given by their peers. Case 1 is as follows:
\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
	\item Each of 1000 students should receive a 90, but the mechanism assigned a 91 to each of them. Maximum deviation is 1, sum is 1000.
	\item Each of 1000 students should receive a 90. One person is assigned a 0, while everyone else is assigned a 90. Maximum deviation is 90, sum is 90.
\end{enumerate}
Clearly, outcome A is better than outcome B. The smaller maximum deviation for outcome A reflects this.
For the maximum work done, consider the the following case:
\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
	\item The professor grades 1000 papers. Maximum work is 1000, sum is 1000.
	\item Each of 1000 students grades 2 papers. Maximum work is 2, sum is 2000.
\end{enumerate}
This time, outcome B is intuitively better than outcome A. Again, the benchmark captures our intuition.

@@

%Repeat above corrections%
\section{Results}
Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested. This is where mechanism design and game theory comes into play. Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose. Then, game theory is used to mathematically predict student behavior to benchmark such a system. Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months. The end result is fairly complete, although there are still questions to be answered in future work.

@@

\subsubsection{Process}
First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we use as a starting point.
One idea is to have the professor choose one paper that he grades. He then distributes this paper to every student, along with a second, ungraded paper. If the students fail to grade the paper the professor graded correctly, they get a 0. If they succeed, they receive their assigned grade.
This is almost exactly the Calibration Mechanism, except we make a small modification. Considering the idea as is, a student whose own grade on the assignment is a 0 has no incentive to grade the paper: Their grade will be a 0 whether or not they grade the paper, so why bother? To cope with this, we pick some minimum grade $m > 0$ and promise every student that they will receive a grade of at least $m$ if they grade the assignment correctly.
By appropriately choosing a value for $m$, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
\begin{definition}(Calibration Mechanism)
First, the professor pre-grades a paper $P$. Each student is asked to grade two papers: $P$ and another paper. If the student fails to grade $P$, he or she gets a zero. Otherwise, the student gets the maximum of some minimum value and his or her assigned grade.
\end{definition}
\begin{theorem}
If $m>H^{-1}(2)$, it will be in every student's best interest to grade both papers in the Calibration Mechanism.
\end{theorem}
\begin{proof}
Consider the student $i$.
If all other students behave as desired, student $i$ will be assigned a grade $G=max(m,o_i)$ unless he or she does not grade $P$ correctly.
The happiness of student $i$ grading one paper is $\frac{H(G)}{2}-1$, because the student has a 50\% chance of getting a 0 and a 50\% chance of getting $G$.
If student $i$ grades both papers, his or her happiness will be $H(G)-2$ because he or she is guaranteed to receive $G$ by grading both correctly.
If student $i$ grades neither, his or her happiness will be $0$, because he or she spends no energy and gets a 0.
Therefore, if $H(G) > 2$, then student $i$ will grade both papers. So, for the professor to guarantee that the class use effort and obtain the correct grades, $H(m) > 2$.
Since we chose $m$ to be greater than $H^{-1}(2)$, the previous always holds.
\end{proof}
\emph{This process is summarized in Figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}

\subsubsection{Benchmark and Remaining Issues}
We now show that the Calibration Mechanism achieves a low value in our benchmark.
\begin{theorem}
The Calibration Mechanism achieves a benchmark score of 4.
\end{theorem}
\begin{proof}
The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value $m$ high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
\end{proof}

@@

This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other. If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.
%%%%%%%% Go over this section and try to make it similar to the above section. %%%%%%%%
\subsection{Improved Calibration Mechanism}
\subsubsection{Process}
In the calibration mechanism, we assumed that students could not communicate with each other, and therefore could not figure out which of the two papers they were asked to grade was calibrated. For this mechanism, we relax this assumption and instead provide a mechanism that works even if each student can communicate with all other students.
\begin{definition}(Improved Calibration Mechanism)
In this mechanism, we apply the Calibration Mechanism on a larger scale. Every student is put into a cycle. Each student grades the papers of $k$ next students. The professor also grades every $kth$ paper in the cycle, which become the calibrated papers. The same system for assigning grades is used as in the calibration mechanism.
\end{definition}
\begin{theorem}
In this mechanism, students will return accurate grades, even though they can communicate with each other.
\end{theorem}
\begin{proof}
In this scheme, because of the overlapping papers, the students have no better way of determining which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students. They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$. This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.

Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers. As long as $m > H^{-1}(k)$, the papers will be accurately graded, as before.

\end{proof}
\subsubsection{Benchmark and Remaining Issues}
The amount of work done by the professor is $\frac{n}{k}$. For the students, this number is $k$. The maximum grade deviation is also $k$, for $m > H^{-1}(k)$. Therefore, the benchmark is $max(k, \frac{n}{k}) + k$, a potentially higher value than before. A downside of the Improved Calibration Mechanism is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$. With a large number of people in a class, this number becomes massive. We can see that the benchmark becomes $2\sqrt{n}$.

\emph{The benchmark results for the Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
%%%%%%%% Revise this section to be like the above. %%%%%%%%
\subsection{Deduction Mechanism}
\label{sec:deduction}
With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions. Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
\subsubsection{Process}
\begin{definition}(Deduction Mechanism)
In this mechanism, each paper is randomly assigned to 2 students. Students deduct as many points as they want, and write a justification for each of them. For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$. Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives the incorrect grader(s) a 0. To compute the final score for a student, the final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$. (Then the student's grade is converted from Happiness to an actual score).
\end{definition}
\begin{theorem}
The addition of the contribution score being added or subtracted should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
\end{theorem}
\begin{proof}
The graders have two choices, they can either grade the papers, or not grade them.

@@

If the student's partner gives the paper a 100, which is the best thing they could do if they do not grade, then
	If they do not grade the paper, they do not use any effort, and their contribution score is 0. So the student's happiness will $H(g) + 4*0 = H(g)$.

If the student grades, he or she uses 1 unit of effort by default, but get the full contribution score of 1. This means that their final happiness is $H(g) + 4\cdot1 - 1 = H(g)+3$.

If the partner gives the paper its true grade:
	If the grader does not grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is $H(g) + 4\cdot(-1) = H(g)-4$.

If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is $H(g) + 4\cdot0 - 1 = H(g)-1$.

In both of the above cases, the happiness outputs for honestly grading the paper is higher than the happiness output when not grading the paper. Our assumptions state that students will do whatever makes them happiest, so they will honestly grade the papers.

\end{proof}
\noindent
\emph{This process is summarized in Figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
\newline
\emph{The benchmark results for the Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
\subsubsection{Benchmark}
In this model, the most work is being done by the students, who each grade 2 papers. In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper. This means that no papers will ever reach the professor, so he or she will not have to grade any papers. Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades. This means that the final benchmark is $2+0=2$. This is the lowest score out of all the mechanisms so far.
\subsection{Final Assumptions}
Now we have a model that accounts for a realistic world view. However, the Deduction Mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders. To address this, we designed a final set of assumptions that more effectively simulate a realistic world.

\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item When grading, $w_i=0 \oplus w_i=1$
	\item For all students, $g_i \neq o_i$
	\item Students all share a common happiness function, $H(g)$, where $g$ represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
	\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
	\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
	\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral
	\item For a given student in $N$, that student has contact with all other students in $N$
\end{enumerate}
\subsection{Comparison}
Figure~\ref{fig:comparison} on page~\pageref{fig:comparison} shows a comparison between our mechanisms and those currently in use. As shown, our mechanisms performs better than the others, aside from the Improved Calibration Mechanism. As can be seen in the figure, the benchmark scores of all traditional methods of grading --- peer grading, hand grading by the professor, and automated grading --- are higher than those our mechanisms. This means that traditional methods result in undesirable outcomes, either inaccurate or requiring a disproportionate amount of work.

>>>>

\documentclass[12pt, Arial]{article}
\title{Teaching a Class to Grade Itself using Game Theory}
\author{}%Nick Kaashoek and William Wu
\date{}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage[section]{placeins}
\usepackage{enumitem}
\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses) and their importance to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}. However, the main importance of MOOCs come from their scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: by the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are simply unable to grade hundreds of thousands of submissions. Currently, two types of solutions are used to remedy the problem: automated grading and peer grading~\cite{edxsoftware}. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers (i.e. multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}. Even though automated grading for written essays is an active area of research with much recent progress, the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}. On the other hand, peer grading can grade any type of question, a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}. These limitations render the students unable to effectively evaluate the mastery of the course material.

@@

The difficulty of the problem lies in finding an incentive to encourage students to spend time grading the assignments of others. Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example. However, this choice may not return a useful result because a clever student will just take the points and assign a generic grade. The professor cannot tell the difference between an accurately assigned 100 and randomly awarded 100. The next step would be to implement simple checking. For example, have each paper be graded by two students who both receive bonus points if their grades match. This may work at first, but clever students will learn over time to coordinate, assign everyone the same grade without doing any work, and pick up the bonus points (again, the professor cannot tell the difference between a randomly or sincerely assigned grade). These examples show that properly incentivizing graders can be a difficult task. The main purpose of this work is to devise mechanisms which avoid these problems, allowing for work to be distributed efficiently.

@@

We start with a simple model and set of assumptions and gradually build upon this set to achieve an increasingly-realistic model. After every change in assumptions, we create a new mechanism that works effectively and efficiently. By the end of our research, we have contributed a highly realistic and detailed model that other game theorists can build off of to form their own solutions, as well as a set of realistic mechanisms that could be implemented in practice.
\section{Materials and Methods}
\subsection{Scenario}
In order to find a solution to the professor's problem, we consider the case of a single assignment. To apply our solution to an entire class, simply apply it to each assignment separately. In a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are the input for a function. Each of these papers, $i$ has an objective score $o_i$ where $0\leq o_i \leq 100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way, with the grades given out being the functions output. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that we use to predict the behavior of the students, we use a set process every time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple mechanisms, which will allow us to evaluate different mechanisms side by side. To begin with, we create this set of assumptions:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students want good grades
	\item Doing work makes students unhappy
	\item Students want to be happy
	\item Students only care about their final happiness
	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
To re-express the above in mathematical terms:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
	\item Students can grade others' work accurately (i.e., they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
	\item Students want to maximize their final happiness, expressed as $H(g)-W$
	\item Students care only about the expectation of their final happiness, which, put in game theoretical terms, makes them risk neutral (i.e., if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
	\item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It does not depend on the score of others
\end{enumerate}

@@

Do these mathematical assumptions perfectly capture human behavior? Of course not. But these assumptions are certainly a meaningful simplification of student behavior, and one should expect mechanisms that are provably good under these assumptions to be pretty good in practice as well.
\subsection{Objective}
The goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment they are given to grade. Without this property, a system becomes unpredictable. In other words, no student can deviate from the desired behavior to improve his or her happiness. In math terms, if by acting honestly student $i$ grades $w_i$ papers and gets a grade of $g_i$ there should not be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.

\subsection{Benchmark}
%Efficiency objective%
A benchmark that will allow different mechanisms to be compared is vital to the iterative process of mechanism development. Mechanisms should be compared in terms of the amount of work done by a person as well as the accuracy of the grades produced. Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desirable outcome. In mathematical terms, we want to minimize the function $\max_{i \ge 1} \{|H(g_i)-H(o_i)|\} + \max_{i \ge 0} \{w_i\}$ in the worst possible case. We call our benchmarking function the \emph{Objective function}, which we use in our research.

@@

In our case, we use the \emph{maximum} deviation and the \emph{maximum} work done. The reason why we do not use the \emph{sum} of the deviations or the \emph{sum} of work done is as follows. Consider the following two cases for the maximum deviation of the grade assigned by the mechanism to the hypothetical professor-given grade. Note that the grade the student receives at the end is not necessarily that given by their peers. Case 1 is as follows:
\begin{enumerate}[label=\Alph*]
	\item Each of 1000 students should receive a 90, but the mechanism assigned a 91 to each of them. Maximum deviation is 1, sum is 1000.
	\item Each of 1000 students should receive a 90. One person is assigned a 0, while everyone else is assigned a 90. Maximum deviation is 90, sum is 90.
\end{enumerate}
Clearly, outcome A is better than outcome B. The smaller maximum deviation for outcome A reflects this.
For the maximum work done, consider the the following case:
\begin{enumerate}[label=\Alph*]
	\item The professor grades 1000 papers. Maximum work is 1000, sum is 1000.
	\item Each of 1000 students grades 2 papers. Maximum work is 2, sum is 2000.
\end{enumerate}
This time, outcome B is intuitively better than outcome A. Again, the benchmark captures our intuition.

@@

%Repeat above corrections%
\section{Results}
Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested. This is where mechanism design and game theory comes into play. Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose. Then, game theory is used to mathematically predict student behavior to benchmark such a system. Starting from the simplest and most obvious approaches, we created, tested, and refined upon various mechanisms in an iterative process that spanned several months. The end result is fairly complete, although there are still questions to be answered in future work.

@@

\subsubsection{Process}
First, we design a mechanism that does extremely well in a model defined by our simple assumptions, which we use as a starting point.
One idea is to have the professor choose one paper that he grades. He then distributes this paper to every student, along with a second, ungraded paper. If the students fail to grade the paper the professor graded correctly, they get a 0. If they succeed, they receive their assigned grade.
This is almost exactly the Calibration Mechanism, except we make a small modification. Considering the idea as is, a student whose own grade on the assignment is a 0 has no incentive to grade the paper: Their grade will be a 0 whether or not they grade the paper, so why bother? To cope with this, we pick some minimum grade $m > 0$ and promise every student that they will receive a grade of at least $m$ if they grade the assignment correctly.
By appropriately choosing a value for $m$, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.\\
\begin{definition}(Calibration Mechanism)
First, the professor pre-grades a paper $P$. Each student is asked to grade two papers: $P$ and another paper. If the student fails to grade $P$, he or she gets a zero. Otherwise, the student gets the maximum of $m$ and his or her assigned grade.
\end{definition}
\medskip
\begin{theorem}
If $m \geq H^{-1}(2)$, it will be in every student's best interest to grade both papers in the Calibration Mechanism.
\end{theorem}
\begin{proof}
Consider the student $i$.
If all other students behave as desired, student $i$ will be assigned a grade $G=max(m,o_i)$ unless he or she does not grade $P$ correctly.
The happiness of student $i$ grading one paper is $\frac{H(G)}{2}-1$, because the student has a 50\% chance of getting a 0 and a 50\% chance of getting $G$.
If student $i$ grades both papers, his or her happiness will be $H(G)-2$ because he or she is guaranteed to receive $G$ by grading both correctly.
If student $i$ grades neither, his or her happiness will be $0$, because he or she spends no energy and gets a 0.
Therefore, if $H(G) > 2$, then student $i$ will grade both papers. So, for the professor to guarantee that the class use effort and obtain the correct grades, $H(m) > 2$.
Since we chose $m$ to be greater than $H^{-1}(2)$, the previous always holds.
\end{proof}
\emph{This process is summarized in Figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}

\subsubsection{Benchmark and Remaining Issues}
We now show that the Calibration Mechanism achieves a low value in our benchmark.\\
\begin{theorem}
The Calibration Mechanism achieves a benchmark score of 4.
\end{theorem}
\begin{proof}
The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value $m$ high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2. This means that the sum is $2+2=4$
\end{proof}

@@

This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other. If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.
%%%%%%%% Go over this section and try to make it similar to the above section. %%%%%%%%
\subsection{Improved Calibration Mechanism}
\subsubsection{Process}
In the calibration mechanism, we assumed that students could not communicate with each other, and therefore could not figure out which of the two papers they were asked to grade was calibrated. For this mechanism, we relax this assumption and instead provide a mechanism that works even if each student can communicate with all other students.\\
\begin{definition}(Improved Calibration Mechanism)
In this mechanism, we apply the Calibration Mechanism on a larger scale. Every student is put into a cycle. Each student grades the papers of $k$ next students. The professor also grades every $kth$ paper in the cycle, which become the calibrated papers. The same system for assigning grades is used as in the calibration mechanism.
\end{definition}
\medskip
\begin{theorem}
In this mechanism, students will return accurate grades as long as $m \geq H^{-1}(k)$, even though they can communicate with each other.
\end{theorem}
\begin{proof}
In this scheme, because of the overlapping papers, the students have no better way of determining which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students. They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(G) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$. This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.

Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers. As long as $m \geq H^{-1}(k)$, the papers will be accurately graded, as before.

\end{proof}
\subsubsection{Benchmark and Remaining Issues}
We now show that the Improved Calibration Mechanism receives a higher benchmark than the calibration mechanism.\\
\begin{theorem}
The Improved Calibration Mechanism achieves a benchmark score of $2\sqrt{n}$.
\end{theorem}
The amount of work done by the professor is $\frac{n}{k}$. For the students, this number is $k$. The maximum grade deviation is also $k$, for $m \geq H^{-1}(k)$. Therefore, the benchmark is $\max\{k, \frac{n}{k}\} + k$, a potentially higher value than before. A downside of the Improved Calibration Mechanism is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$. With a large number of people in a class, this number becomes massive. We can see that the benchmark becomes $2\sqrt{n}$.

\emph{The benchmark results for the Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
%%%%%%%% Revise this section to be like the above. %%%%%%%%
\subsection{Deduction Mechanism}
\label{sec:deduction}
With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions. Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
\subsubsection{Process}
\begin{definition}(Deduction Mechanism)
In this mechanism, each paper is randomly assigned to 2 students. Students deduct as many points as they want, and write a justification for each of them. For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$. If $x_i = x_j = 0$ both contribution scores are $\frac{1}{2}$. Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives the incorrect grader(s) a 0. To compute the final score for a student, the final grade on the assignment is calculated as follows: 2 points times their contribution score are added to $H(g)$. (Then the student's grade is converted from Happiness to an actual score).
\end{definition}
\medskip
\begin{theorem}
The addition of the contribution score being added encourages graders to honestly grade papers.
\end{theorem}
\begin{proof}
The graders have two choices, they can either grade the papers, or not grade them.

@@

If the student's partner gives the paper a 100, which is the best thing they could do if they do not grade, then
	if the student does not grade the paper, they do not use any effort, and their contribution score is $\frac{1}{2}$. So the student's happiness will $H(g) + 2\cdot0.5 = H(g)+1$.

If the student grades, he or she uses 1 unit of effort by default, but will get the full contribution score of 1. This means that their final happiness is $H(g) + 2\cdot1 - 1 = H(g)+1$.

If the partner gives the paper its true grade:
	If the grader does not grade the assignment, they will give it a 100 and so the grader's contribution score is 0. So their happiness is $H(g) + 2\cdot0 = H(g)$.

If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is $H(g) + 2\cdot0.5 - 1 = H(g)$.

In both of the above cases, the happiness output for honestly grading the paper is equal to the happiness output when not grading the paper. However, if we increase the 2 present in each equation by an infinitely small amount, the equalities become strict, and as our assumptions state that students will do whatever makes them happiest, so they will honestly grade the papers. For our purposes, because this new coefficient is greater than 2 by an infinitely small amount, we simply refer to it as 2.

\end{proof}
\noindent
\emph{This process is summarized in Figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
\newline
\emph{The benchmark results for the Deduction Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
\subsubsection{Benchmark}
We now show that the Deduction Mechanism receives the lowest benchmark out of our three mechanisms.\\
\begin{theorem}
The Deduction Mechanism achieves a benchmark score of $4$.
\end{theorem}
In this mechanism, the most work is being done by the students, who each grade 2 papers, while the professor will not perform any work, because students will adhere to the dominant strategy behavior, honestly grading the papers. This means that no papers will ever reach the professor, so he or she will not have to grade any papers, making the most work done by any one person $2$. Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 2, since every student will output accurate grades, but also get a bonus 2 points thanks to the reward. This means that the final benchmark is $2+2=4$.
\subsection{Final Assumptions}
Now we have a model that accounts for a realistic world view. However, the Deduction Mechanism still has some unrealistic parts. To address this, we designed a final set of assumptions that more effectively simulate a realistic world.
